---
title: "Real test"
teaching: 10
exercises: 2
---

:::::::::::::::::::::::::::::::::::::: questions 

- How do you know which packages you used? 

::::::::::::::::::::::::::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::: objectives

- Print out the packages used in a session. 

::::::::::::::::::::::::::::::::::::::::::::::::

## Conclusion

Reproducibility!!

::::::::::::::::::::::::::::::::::::: challenge 

## Challenge 1: Can you do it?

What is the output of this command?

```{r, eval = FALSE}
sessionInfo()
```

:::::::::::::::::::::::: solution 

## Output
 
```{r, echo = FALSE}
sessionInfo()
```

:::::::::::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::::::::::::::


This tells you everything you need!!

::::::::::::::::::::::::::::::::::::: keypoints 

- Use `.Rmd` files for lessons even if you don't need to generate any code
- Run `sandpaper::check_lesson()` to identify any issues with your lesson
- Run `sandpaper::build_lesson()` to preview your lesson locally

::::::::::::::::::::::::::::::::::::::::::::::::

<!-- Please do not delete anything below this line -->

```{r links, child = sandpaper::template_links()}
```
